---
title: "R Notebook"
output: html_notebook
---

```{r}
#load in packages
library(terra)
library(tidyverse)
library(tidyterra)
```

```{r}
wgbt2020_2011 <- rast("~/Global Change Geography MSc/SoSe 25/Applied Geoinformation Science/Block2/climate-model-output/WBGT_dayover28_2011_2020_present.tif")

wgbt2021_2030 <- rast("~/Global Change Geography MSc/SoSe 25/Applied Geoinformation Science/Block2/climate-model-output/WBGT_dayover28_2011_2020_present.tif")

wgbt2020_2011 <- rast("~/Global Change Geography MSc/SoSe 25/Applied Geoinformation Science/Block2/climate-model-output/WBGT_dayover28_2011_2020_present.tif")
wgbt2020_2011 <- rast("~/Global Change Geography MSc/SoSe 25/Applied Geoinformation Science/Block2/climate-model-output/WBGT_dayover28_2011_2020_present.tif")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
